Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-13 hscc2017/paper.tex
explained the presence of uncertainty in the experimental evaluation

For the majority of the benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine is able to find a stable solution in less than one minute for half
of the benchmarks. This is possible if the inductive solutions need to be 
refined with few counterexamples and increments of the fixed-point precision.  
However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$) has 
required too many counterexamples to refine its solution.  
For this particular case, the one-stage engine is able to complement the
two-stage approach and synthesize a solution instead.  It is important to
reiterate that the one-stage verification engine does not take advantage of
the inductive conjecture inherent to CEGIS, but instead fully explores the
counterexample space in one SAT instance.  As expected, this approach is 
significantly slower on average and is only useful for benchmarks where 
the CEGIS approach requires too many counterexample refinement iterations
such that exploring all counterexamples in a single SAT instance performs better.
Our results suggest an average performance difference of at least two orders
of magnitude between the two engines, leading to the one-stage engine timing
out on the majority of our benchmarks.  Table~\ref{tab:results}
lists the results for both engines, where in $16$ out of $23$
benchmarks the two-stage engine is faster.

@@

\blue{[The presence of uncertainty is not explained in this description and should be clearly elaborated and commented over the results in the Table.]}

Considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
the median run-time amounts to $48$\,s, implying that \tool can synthesize half of the controllers 
in less than one minute. Overall, the average fastest synthesis time considering
both engines is approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine, which is faster for two benchmarks where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers have been confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2. 
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
CBMC (SHA-1 hash) version: 7a6cec1dd0eb8843559591105235f1f2c4678801}

>>>>

For the majority of the benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine is able to find a stable solution in less than one minute for half
of the benchmarks. This is possible if the inductive solutions need to be 
refined with few counterexamples and increments of the fixed-point precision.  
However, the benchmark \emph{SatelliteB2} with uncertainty ($G_{3b}$) has 
required too many counterexamples to refine its solution.  
For this particular case, the one-stage engine is able to complement the
two-stage approach and synthesize a solution instead.  It is important to
reiterate that the one-stage verification engine does not take advantage of
the inductive conjecture inherent to CEGIS, but instead fully explores the
counterexample space in one SAT instance.  As expected, this approach is 
significantly slower on average and is only useful for benchmarks where 
the CEGIS approach requires too many counterexample refinement iterations
such that exploring all counterexamples in a single SAT instance performs better.
Our results suggest an average performance difference of at least two orders
of magnitude between the two engines, leading to the one-stage engine timing
out on the majority of our benchmarks.  Table~\ref{tab:results}
lists the results for both engines, where in $16$ out of $23$
benchmarks, the two-stage engine is faster.

@@

The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$) 
leads to harder verification conditions to be checked 
by the {\sc verify} phase, which thus influences the overall synthesis time. 
However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
the median run-time amounts to $48$\,s, implying that \tool can synthesize 
half of the controllers in less than one minute. Overall, the average fastest synthesis 
time considering both engines is approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine, which is faster for two benchmarks where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers have been confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2. 
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
CBMC (SHA-1 hash) version: 7a6cec1dd0eb8843559591105235f1f2c4678801}
